Poker Chips, Earthquakes, and Computation

### 2014-10-13 finaldraft.tex
fixed typos
fixed more typos

In Section~\ref{Definitions and Notation}, we formalize the terminology and operations we use to analyze the problem. In particular, we formalize the effects of earthquakes, as well as what it means for a board of chips to be finite or infinite. 
In Section~\ref{Stability of Finite Boards}, we introduce a spread function that maps finite board configurations to positive integers. 
We then use the fact that earthquakes strictly increase the value of this spread function to show that finite boards cannot cycle back to previous configurations. We also show that the number of possible configurations a finite board can be transformed into by earthquake is bounded. These two results together will show that all finite boards reach a steady state. 
In Section~\ref{Order of Redistribution}, we show that for a given board the number of times a particular square must be hit by a earthquake in order for a board to stabilize is independent of the order in which the earthquakes occur.

@@

\begin{theorem} If $b$ is a finite board that is repeatedly hit by earthquakes, it must eventually reach a stable state. 
\end{theorem}
\label{finitestability}
\begin{proof}
Lemma~\ref{finiteextension} implies that there a finite board with $C$ total chips can only ever occupy a finite number $D$ of squares. This implies a finite upper bound of $\binom{D+C-1}{D-1}$ possible boards (via an elementary combinatorics argument of how to distribute $C$ identical objects among $D$ distinguishable slots).

@@

We first introduce conventional definitions of boolean variables and functions.
\begin{definition} 
A Boolean variable is a number in $\{0,1\}$, and a Boolean function is a function that takes in a finite number of Boolean variable and outputs a Boolean variable.
\end{definition}

>>>>

In Section~\ref{Definitions and Notation}, we formalize the terminology and operations we use to analyze the problem. In particular, we formalize the effects of earthquakes, as well as what it means for a board of chips to be finite or infinite. 
In Section~\ref{Stability of Finite Boards}, we introduce a spread function that maps finite board configurations to positive integers. 
We then use the fact that earthquakes strictly increase the value of this spread function to show that finite boards cannot cycle back to previous configurations. We also show that the number of possible configurations a finite board can be transformed into by earthquakes is bounded. These two results together will show that all finite boards reach a steady state. 
In Section~\ref{Order of Redistribution}, we show that for a given board the number of times a particular square must be hit by an earthquake in order for a board to stabilize is independent of the order in which the earthquakes occur.

@@

\begin{theorem} If $b$ is a finite board that is repeatedly hit by earthquakes, it must eventually reach a stable state. 
\end{theorem}
\label{finitestability}
\begin{proof}
Lemma~\ref{finiteextension} implies that a finite board with $C$ total chips can only ever occupy a finite number $D$ of squares. This implies a finite upper bound of $\binom{D+C-1}{D-1}$ possible boards (via an elementary combinatorics argument of how to distribute $C$ identical objects among $D$ distinguishable slots).

@@

We first introduce conventional definitions of Boolean variables and functions.
\begin{definition} 
A Boolean variable is a number in $\{0,1\}$, and a Boolean function is a function that takes in a finite number of Boolean variable and outputs a Boolean variable.
\end{definition}
